### 2014-10-12 writing/AAAI SSS '15/join.tex
Add final results to paper; related configs

\paragraph{Results} 
We found that the NTN model worked best with 11-dimensional vector
representations for the 80 sets and a 90-dimensional feature vector
for the classifier, though the performance of the model was not highly
dependant on either dimensionality setting. 
This model was able to correctly label 99.4\% (94.3
macroaveraged F1) of the provably derivable test examples, and 95.4\%
(92.2 macro-F1) of the remaining test examples. The simpler NN worked
best with 11 and 75 dimensions, respectively, but was able to achieve
accuracies of only 89.0\% (80.7 macro-F1) and 62.5\% (40.7 macro-F1),
respectively. Training accuracy was 99.8\% for the NTN and 95.4\% for
the NN.

>>>>

\paragraph{Results} 
We found that the NTN model worked best with 11-dimensional vector
representations for the 80 sets and a 90-dimensional feature vector
for the classifier, though the performance of the model was not highly
dependant on either dimensionality setting. 
Averaging over five randomly generated datasets, the model was able to correctly label 98.1\% (standard deviation $\sigma = 1.5\%$) of the provably derivable test examples, and 87.7\%
($\sigma = 8.0\%$) of the remaining test examples. The simpler NN worked
best with 11 and 75 dimensions, respectively, but was able to achieve
accuracies of only 84.8\% ($\sigma = 1.9\%$) and 68.7\% ($\sigma = 3.5\%$),
respectively. Training accuracy was 99.8\% ($\sigma = 0.1\%$) for the NTN and 94.7\% ($\sigma = 2.0\%$) for
the NN.

### 2014-10-12 writing/AAAI SSS '15/methods.tex
Add final results to paper; related configs

We build an embedding-based model using the method of
\cite{Bowman:Potts:Manning:2014}, which is centered on the task of
labeling a pair of words or sentences with one of a small set of
logical relations. The architecture of the model that we use, which is
limited to only pairs of single symbols (such as words), is depicted
in Figure~\ref{sample-figure}. The model represents the two input
symbols as embeddings, which are fed into a comparison function based
on one of two types of neural network layer functions to produce a
representation for the relationship between the two symbols. This
representation is then fed into a softmax classifier, which outputs a
distribution over possible labels. The entire network, including the
embeddings, are trained using backpropagation.

@@

This model used here differs from the one described in that work in
two ways. Because the inputs are single symbols, we do not use
a composition function here. Also, for our experiment on WordNet data, 
we introduce an additional neural network layer between the embedding 
input and the comparison function, which facilitates initializing the 
embeddings themselves from pretrained vectors and was found to help 
performance in that setting.

>>>>

We build an embedding-based model using the method of
\cite{Bowman:Potts:Manning:2014}, which is centered on the task of
labeling a pair of words or sentences with one of a small set of
logical relations. The architecture of the model that we use, which is
limited to only pairs of single terms (such as words), is depicted
in Figure~\ref{sample-figure}. The model represents the two input
terms as embeddings, which are fed into a comparison function based
on one of two types of neural network layer functions to produce a
representation for the relationship between the two terms. This
representation is then fed into a softmax classifier, which outputs a
distribution over possible labels. The entire network, including the
embeddings, are trained using backpropagation.

@@

This model used here differs from the one described in that work in
two ways. Because the inputs are single terms, we do not use
a composition function here. Also, for our experiment on WordNet data, 
we introduce an additional neural network layer between the embedding 
input and the comparison function, which facilitates initializing the 
embeddings themselves from pretrained vectors and was found to help 
performance in that setting.

### 2014-10-12 writing/AAAI SSS '15/wordnet.tex
Add final results to paper; related configs

\paragraph{Results} 
We find that the NTN performs almost perfectly even when trained only
on a fraction of the ground truth relations. The plain NN is somewhat less
successful. Neither model has reached perfect performance in any of
our experiments, though we are continuing to tune both models.

\begin{table}[h]
\centering\resizebox{5.5in}{!}{
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{r r@{ }r r@{ }r r@{ }r r@{ }r r@{ }r} 
    \toprule
     Portion of & \multicolumn{4}{c}{NN} & \multicolumn{4}{c}{NTN} & \multicolumn{2}{c}{Baseline}\\
     training data  & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} \\
    \midrule
     100\%   & 99.5 &(100.0) & 98.9 &(99.7)    & \textbf{99.6} &(100.0) & 99.2 &(100.0) & 37.9 &(--)\\
     33\%    & 96.0 &(100.0) & 37.0 &(37.0)    & 95.4 &(100.0)          & 95.3 &(100.0) & 37.9 &(--)\\
     11\%    & 91.8 &(100.0) & 91.9 &(100.0)   & 92.1 &(99.7)           & 92.2 &(100.0) & 37.9 &(--)\\
     % 2\%    & 86.0 &(100.0) & ... &(100.0)   & 86.2 &(100.0)           & 76.4 &(87.3) & 37.9 &(--)\\ % Accidental run with slightly different train/test split.
    \bottomrule
  \end{tabular}}
 \caption{Test (train) accuracy figures on the WordNet data. The baseline figure is simply the frequency of the most frequent class, \ii{coordinate}.\label{b-table}}  
\end{table}

>>>>

\paragraph{Results} 
We find that the NTN performs perfectly with random initialization, and that the plain NN performs almost as well. We also find that initialization with GloVe is helpful in allowing the models to maintain fair performance
with smaller amounts of training data. Some of the randomly initialized model runs failed to learn
usable representations at all and labeled all examples with the most frequent labels. We excluded these runs from the statistics, but marked settings for which this occurred with the symbol $\dagger$. For all of the remaining runs, training accuracy was consistently above 99\%.

\begin{table}[h]
\centering\resizebox{5.5in}{!}{
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{r r@{ }r r@{ }r r@{ }r r@{ }r r@{ }r} 
    \toprule
     Portion of & \multicolumn{4}{c}{NN} & \multicolumn{4}{c}{NTN} & \multicolumn{2}{c}{Baseline}\\
     training data  & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} \\
    \midrule
     100\%   & 99.7 &(0.0) & 99.4$^\dagger$ &(0.3)    & 99.6 &(0.0) & \textbf{100.0} &(0.1) & 37.9 &(--)\\
     33\%    & 96.0 &(0.5) & 95.3 &(0.2)     & 95.8 &(0.8)          & 95.5$^\dagger$ &(0.5) & 37.9 &(--)\\
     11\%    & 91.1 &(0.5) & 90.8$^\dagger$ &(0.3)    & 91.3 &(0.6)          & 90.9$^\dagger$ &(0.2) & 37.9 &(--)\\
     % 2\%    & 86.0 &(100.0) & ... &(100.0)   & 86.2 &(100.0)           & 76.4 &(87.3) & 37.9 &(--)\\ % Accidental run with slightly different train/test split.
    \bottomrule
  \end{tabular}}
 \caption{Mean test \% accuracy scores (with standard deviations) on the WordNet data over five-fold crossvalidation. The baseline figure is simply the frequency of the most frequent class, \ii{coordinate}.\label{b-table}} 
\end{table}
